Untitled

### 2025-03-14 script/r/discontinuity_plot.Rmd
maj discontinuity plot

```{r}
df_40 <- read_dta("data/data_dta/df_40_2.dta")

df_40 <- na.omit(subset(df_40, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num")))

reg3_40 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num), clusters = cluster_bdd, data = df_40)

library(lfe)

reg3_40 <- felm(pol_trust ~ dist_cap_max_norm + dist_sndncap_max_norm + age + age_2 + factor(sex) + factor(educ_sec) + 
              factor(bin_rural) + factor(bin_conditions_eco) + factor(bin_conditions_country) + factor(bin_emp) + disc_pol_a + 
              tele_news + paper_news + radio_news + night_region_log + pop_region_log + area_region_log | 
              country_round + murdock_names | 0 | cluster_bdd, data = df_40)
summary(reg3_40)

df_40$ft_values <- fitted(reg3_40)

@@

#On crée une base avec les gens près et une avec les gens loin
df_40_pres <- subset(df_40, df_40$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
df_40_loin <- subset(df_40, df_40$distance_border>0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)

#On définit 10 intervalles
nb_intervals <- 10

@@

```{r}
theme_set(theme_minimal(base_family = "Arial"))

ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  scale_color_manual(values = c("blue", "red"), 
                     name = "Legend",
                     labels = c("Close to the capital","Far to the capital")) + 
  labs(x = "Distance from the Border (in km)",
       y = "Political Trust") +
  scale_x_continuous(labels = function(x) x / 1000) +

  theme_minimal() +

  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +

    geom_point(aes(color = mean_dist_border_intervals > 0), size=3, show.legend = FALSE) +

  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
              method = "lm", formula = y ~ poly(x, 2), color = "darkblue", size = 1, se = TRUE,
    level = 0.90, show.legend = FALSE) +

  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
              method = "lm", formula = y ~ poly(x, 2), color = "darkred", size = 1, se = TRUE,
    level = 0.90,
show.legend = FALSE) +

  geom_segment(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)), 
                   xend = 0, 
                   y = moy_trust_pres, 
                   yend = moy_trust_pres, 
                   linetype = "mean_near"),
               color = "darkblue", size = 1.5) +

  geom_segment(aes(x = 0, 
                   xend = max(abs(data_intervals$mean_dist_border_intervals)), 
                   y = moy_trust_loin, 
                   yend = moy_trust_loin, 
                   linetype = "mean_far"),
               color = "darkred", size = 1.5) +

scale_linetype_manual(name = NULL, 
                        values = c("mean_near" = "solid", 
                                   "mean_far" = "solid"),
                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), max(abs(data_intervals$mean_dist_border_intervals))))+

ggtext::geom_richtext(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Close to the Capital"),
                        vjust = 2, hjust = 0.6, size = 5, fill = "white", color = "black", fontface = "bold", 
                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) + 
  ggtext::geom_richtext(aes(x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Far from the Capital"),
                        vjust = 2, hjust = 0.4, size = 5, fill = "white", color = "black", fontface = "bold", 
                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) +

  theme(plot.title = element_text(size = 20, hjust = 0.5),  
        axis.title = element_text(size = 15), 
        legend.text = element_text(size = 12),
        legend.position = c(0.85, 0.2), # Position de la légende
        legend.background = element_rect(fill = alpha('white', 1)))

ggsave("plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)

```{r}
# Set the base theme
theme_set(theme_minimal(base_family = "Arial"))

# Create the plot
ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  # Add color scale
  scale_color_manual(
    values = c("blue", "red"), 
    name = "Legend",
    labels = c("Close to the capital", "Far to the capital")
  ) +

  # Add labels and scales
  labs(
    x = "Distance from the Border (in km)",
    y = "Political trust"
  ) +
  scale_x_continuous(labels = function(x) x / 1000) +
  theme_minimal() +

  # Add vertical line at x=0
  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +

  # Add points
  geom_point(
    aes(color = mean_dist_border_intervals > 0), 
    size = 3, 
    show.legend = FALSE
  ) +

  # Add smooth lines for both sides
  geom_smooth(
    data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
    method = "lm", 
    formula = y ~ poly(x, 2), 
    color = "darkblue", 
    size = 1,
    show.legend = FALSE
  ) +
  geom_smooth(
    data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
    method = "lm", 
    formula = y ~ poly(x, 2), 
    color = "darkred", 
    size = 1,
    se = TRUE,
    level = 0.90,
    show.legend = FALSE
  ) +

  # Add mean lines
  geom_segment(
    aes(
      x = -max(abs(data_intervals$mean_dist_border_intervals)), 
      xend = 0, 
      y = moy_trust_pres, 
      yend = moy_trust_pres, 
      linetype = "mean_near"
    ),
    color = "darkblue", 
    size = 1.5
  ) + 
  geom_segment(
    aes(
      x = 0, 
      xend = max(abs(data_intervals$mean_dist_border_intervals)), 
      y = moy_trust_loin, 
      yend = moy_trust_loin, 
      linetype = "mean_far"
    ),
    color = "darkred", 
    size = 1.5
  ) +

  # Add line type scale
  scale_linetype_manual(
    name = NULL, 
    values = c("mean_near" = "solid", "mean_far" = "solid"),
    labels = c(expression(bar(y)[far]), expression(bar(y)[close]))
  ) +

  # Set coordinate limits
  coord_cartesian(
    xlim = c(
      -max(abs(data_intervals$mean_dist_border_intervals)), 
      max(abs(data_intervals$mean_dist_border_intervals))
    )
  ) +

  # Add text labels
  ggtext::geom_richtext(
    aes(
      x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
      y = Inf, 
      label = "Close to the Capital"
    ),
    vjust = 2, 
    hjust = 0.6, 
    size = 5, 
    fill = "white", 
    color = "black", 
    fontface = "bold", 
    label.color = "black", 
    box.padding = unit(0.5, "lines"), 
    label.size = 1
  ) + 
  ggtext::geom_richtext(
    aes(
      x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
      y = Inf, 
      label = "Far from the Capital"
    ),
    vjust = 2, 
    hjust = 0.4, 
    size = 5, 
    fill = "white", 
    color = "black", 
    fontface = "bold", 
    label.color = "black", 
    box.padding = unit(0.5, "lines"), 
    label.size = 1
  ) +

  # Theme customization
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title = element_text(size = 15),
    legend.text = element_text(size = 12),
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(fill = alpha('white', 1))
  )
```

>>>>

```{r}
df_40 <- read_dta("data/data_dta/df_40.dta")

df_40%<>%
  group_by(id_unique)%>%
  mutate(mountain_region_tv=mountain_region*tv,
         desert_region_tv=desert_region*tv) %>%
  ungroup()

df_40 <- na.omit(subset(df_40, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))

reg3_40 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv, clusters = cluster_bdd, data = df_40)

summary(reg3_40)

df_40$ft_values <- fitted(reg3_40)
```

@@

#On crée une base avec les gens près et une avec les gens loin
df_40_pres <- subset(df_40, df_40$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
df_40_loin <- subset(df_40, df_40$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)

#On définit 10 intervalles
nb_intervals <- 40

@@

```{r}
# Create modified datasets with points at the boundary and extremes
data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)

# Find the min and max values in your x range
x_min <- -40000  # -40 km in your units
x_max <- 40000   # 40 km in your units

# Find the predicted values at x=0, x_min, and x_max for each curve
left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)

y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))

y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))

# Average confidence interval for the added points
avg_ic_left <- mean(data_left$ic_trust)
avg_ic_right <- mean(data_right$ic_trust)

# Add points at x=0 and x=x_min to left dataset
data_left_plus <- rbind(data_left, 
                        data.frame(
                          mean_dist_border_intervals = 0,
                          mean_trust_intervals = y_at_zero_left,
                          ic_trust = avg_ic_left
                        ),
                        data.frame(
                          mean_dist_border_intervals = x_min,
                          mean_trust_intervals = y_at_min,
                          ic_trust = avg_ic_left
                        ))

# Add points at x=0 and x=x_max to right dataset
data_right_plus <- rbind(data_right, 
                         data.frame(
                           mean_dist_border_intervals = 0,
                           mean_trust_intervals = y_at_zero_right,
                           ic_trust = avg_ic_right
                         ),
                         data.frame(
                           mean_dist_border_intervals = x_max,
                           mean_trust_intervals = y_at_max,
                           ic_trust = avg_ic_right
                         ))
```

```{r}
ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  # Add vertical line at border
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.8) +

  # Left side smooth curve (Close to Capital)
# Left side smooth curve (Close to Capital)
geom_smooth(data = data_left_plus,
            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
            method = "lm", formula = y ~ poly(x, 3), 
            color = "navy", size = 1.2, se = TRUE,
            fill="navy",
            alpha=0.1,
            level = 0.90, show.legend = FALSE) +

# Right side smooth curve (Far from Capital)
geom_smooth(data = data_right_plus,
            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
            method = "lm", formula = y ~ poly(x, 3), 
            color = "firebrick", size = 1.2, se = TRUE,
            fill = "firebrick",
            alpha = 0.1,
            level = 0.90, show.legend = FALSE)+

geom_segment(aes(x = -40000, 
                   xend = 0,
                   y = moy_trust_pres, 
                   yend = moy_trust_pres, linetype = "Close"),
             inherit.aes = FALSE,
             color = "navy", size = 1.5, alpha = 0.7, data = data.frame()) + 
  geom_segment(aes(x = 0, 
                   xend =40000, 
                   y = moy_trust_loin, 
                   yend = moy_trust_loin, linetype = "Far"),
               inherit.aes = FALSE,
               color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) +

    # Add annotations in better positions with borders

  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
           label = "Close to the Capital", 
           size = 7, fill = "aliceblue", color = "navy", fontface = "bold", 
           label.size = 0.5, family = "Arial") +
  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
           label = "Far from the Capital", 
           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
           label.size = 0.5, family = "Arial") +

  # Add legend for mean lines
  scale_linetype_manual(name = NULL, 
                        values = c("Far" = "dashed", 
                                  "Close" = "dashed"),
                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +

  # Set appropriate axis limits
  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
                          max(abs(data_intervals$mean_dist_border_intervals))),
                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +

  # Format axes
  scale_x_continuous(labels = function(x) x / 1000,
                    breaks = seq(-40000, 40000, 10000)) +

  # Add clear labels
  labs(x = "Distance from the Border (in km)",
      y = "Political Trust") +
      #title = "Border Discontinuity in Political Trust",
      #subtitle = "Comparing areas close to vs. far from the capital") +

  # Polish theme
  theme_minimal()+
  theme(
  text = element_text(family = "Arial"),
    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)), 
    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 30)),
    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 30)),
    axis.text = element_text(size = 11),
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 20),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank(),
    plot.margin = margin(t = 20, r = 20, b = 20, l = 20)
  )

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
```
